A Machine Learning Approach to MLB Catcher Framing

### 2021-12-09 Slides.Rmd
Added variables and a bit to the other intro slides

- "Catcher framing is the art of a catcher receiving a pitch in a way that makes it more likely for an umpire to call it a strike -- whether that's turning a borderline ball into a strike, or not losing a strike to a ball due to poor framing." - MLB.com Glossery

@@

- Baseball Catcher's can influence the call of a ball or strike on how they catch the ball
- Some catcher's are better than others at this skill
- Baseball teams are aware of this and are acquiring players good at this skill to win more games
- We want to quantify the best catcher's at framing for the 2021 season
- There are several factors that influence whether a pitch will be a strike or ball

@@

- which variables used and why

>>>>

- "Catcher framing is the art of a catcher receiving a pitch in a way that makes it more likely for an umpire to call it a strike -- whether that's turning a borderline ball into a strike, or not losing a strike to a ball due to poor framing." - MLB.com Glossary

@@

- Baseball catchers can influence the call of a ball or strike on how they catch the ball
- Some catchers are better than others at this skill
- Baseball teams are aware of this and are acquiring players good at this skill to win more games
- We want to quantify the best catcher's at framing for the 2021 season
- There are several factors that influence whether a pitch will be a strike or ball
- Catchers getting more strikes translates to more outs, and fewer points for the opposing team

@@

- We used:
- Pitch type and pitch release speed, position, and spin rate
- Whether or not the pitcher and batter are right or left handed
- Count, number of outs during the at-bat, and inning number
- Where the pitch landed
- Whether the game was played home or away
